\thesistitle

### 2019-07-22 sections/experimentalsetup.tex
Common interface

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same Method}: All instances of the clone class are in the same method.
  \item \textbf{Same Class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
  \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

@@

\begin{equation}\label{eq:sameclass}
((x)(x + 1) / 2) * y
\end{equation}

@@

Cloned nodes are flagged as \textit{Superclass} if the classes in which these clones are found are parent and child class of each other. Here, the classes of these nodes follow the same definition as stated in the previous section.

Cloned nodes are flagged as \textit{Siblings} if the classes in which these clones are found all share the same parent and this parent class is not external.

Cloned nodes are flagged as \textit{First Cousin} if the classes in which these clones are found all share the same parent and this parent class is not external.

\subsubsection{Common Interface}
\todo{TODO}

>>>>

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same Method}: All instances of the clone class are in the same method.
  \item \textbf{Same Class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

@@

\begin{equation}\label{eq:sameclass}
\frac{x * (x + 1)}{2} * y
\end{equation}

@@

Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other. Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external. Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.

Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent. Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.

\subsubsection{Common Interface}
Many object-oriented languages know the concept of ``interfaces'', which are used to specify a behavior that classes must implement. As code clones describe functionality and interfaces originally did not allow for functionality, interfaces did not open up refactoring opportunities for duplicated code. However, many programming languages nowadays support default implementations in interfaces. Since Java 7 and C\#8, these programming languages allow for functionality to be defined in interfaces. Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.

The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract. That is, all functionality that is shared between classes via an interface cannot be hidden by setting a stricter visibility. Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.

To check whether two cloned nodes have common interfaces, we recursively walk all types the class or interface of the cloned nodes implement and extend. The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.

### 2019-07-22 sections/related_work.tex
Common interface

\chapter{Related work}
\label{ch:related_work}
We divide the related work into ... categories:  ...

>>>>

\chapter{Related work} \label{ch:related_work}
\todo{Rewrite this part and add a lot of content}
The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}. DCRA only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair. We further look into these measurements in Sec.~\ref{chap:relationsinstances}.

A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones. They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}. This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.

We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, all of these tools only support a subset of all harmful clones that are found. Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.
